---
title: "Disabiliy Across Seattle"
author: "Sophie Hurst, Katie Brower, Emily Kong, Hailey Meister"
date: "5/21/2019"
output: html_document
---

```{r setup, include=FALSE}
library("knitr")
knitr::opts_chunk$set(echo = FALSE)
source("./scripts/neighborhoods.R")
source("scripts/summary.R")
source("scripts/summary_table.R")
age_data <- read.csv("./data/aging-and-disability-services-client-level-data-2016.csv", stringsAsFactors = FALSE)
```

## Disability in the United States

Looking at **disability across the United States**, we have found data to understand where there may be defecits in accessibility for disabled people. This includes looking at specific groups of people that may need the most accessibility based on their level of ability to perform certain tasks. The dataset described in this report is from Seattle City's Aging and Disability Services department. The data collected based on City of Seattle neighborhoods and broken down by age range and ability to do daily tasks, and includesinformation on race, ethnicity, and housing status.This gives a good idea of how prevalent disability is in the city of _Seattle, WA_ and which physical locations may need the most attention when it comes to providing accessibility. 

## Summary of Data
```{r summary_list, echo=FALSE, include=FALSE}
summary_list <- summary_info(age_data)
```

This set of data inclues `r summary_list$length` distinct pieces of information for `r summary_list$height` separate people in the city of Seattle. It spans 20 different neighborhoods within the city limits which are, `r summary_list$locations`. Each person is given a code to represent their stated race which is `r summary_list$race`. Those codes are as follows; 1 - American Indian or Alaska Native, 2 - Asian, Asian-American, 3 - Black, African American, Other African, 4 - Hawaiian Native or Pacific Islander, 5 - Hispanic, Latino, 6 - White or Caucasian, 7 - Other, 8 - Multi-Racial, or NA - Not Available. Finally, the data shows the prevalence of disability in the Seattle area, with each person bgin marked as Y - yes they have a disability, N - no they do not have a disability, or U - unknown. The most prevalent marker in the dataset is `r summary_list$disability` showing that more people have a disability than do not in the data collected.

## Table of Summary Information
```{r sum_table, echo=FALSE}
kable(summary_table(age_data), col.names = c("Age Range", "Number of People", "Most Prevalent Income Bracket", "Most Prevalent Race", "Number of Disability Types"))
```

## Disability and Homelessness
From the bar char below one can see which **Seattle neighborhood** has the most people with disabilities. When scrolled over each bar shows which neighborhood was hovered over, the exact number of disabled people, and the exact number of people that are _disabled_ and _homeless_. The bar chart makes it clear which Seattle neighborhood has the **highest population** of people with disabilities the added color gradient makes it clear which neighborhood has the highest number of homeless people with disabilities. From this data one can see that there is a flaw provided acessability for people with disabilities because there are so many homeless people with disabilities in Seattle, WA. 
`r bar_chart(age_data)`
